The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
win len proper interpret points

* increasing window length = increasingly similar
*

>>>>

* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
* layers are more similarly relevant at high window length
